---
title: "Lab 8 ESM 206"
author: "Alia Ajina"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

### Read in slo_homes.csv data

```{r}
homes <- read_csv(here("data", "slo_homes.csv"))
```

unique(homes$city) in the consule will return a list of all of the cities in the data set

### Creat a subset with 4 cities

Task: create a subset (called homes_subset) that only contains observations where the city is:
- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Maria-Orcutt"

If i were to use a double equal symbol, ==, it would only return things in the specific order, it wouldn't check every row for all of these options, so we use the in operator; %in%

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration

Task: create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

using eval = FALSE means the code won't run at all, if you use this code chunk in the future, don't use eval = FALSE, include = FALSE means it wont show up in your knitted document

```{r, include = FALSE, eval = FALSE}
homes_subset %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = round(mean(Price), 1),
            sd_price = round(sd(Price), 1),
            mean_sqft = round(mean(SqFt), 1))
```

Task: Explore the relationship between square footage and home price (from homes_subset) in a scatterplot.

Overall this follows a linear relationship with a positive relationship between sqaure footage and home prices on average.

Outlier? Maybe location, amount of land, or view

If there are outliers, we need to think about possible explanations for them

```{r}
ggplot(data = homes_subset, 
       aes(x = SqFt, y = Price)) + 
  geom_point(color = "#801B1B") + 
  theme_minimal() + 
  geom_smooth(method = "lm", color = "black")
```

### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price

Task: Create 2 different permutations of this model:
1. Price as a function of City, Bedrooms, Bathrooms, SqFt, Status - lm 1
2. Price - City, SqFt, Status - lm 2
3. Price - City - lm 3

```{r}
lm_1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)

lm_2 <- lm(Price ~ City + SqFt + Status, data = homes_subset)

lm_3 <- lm(Price ~ SqFt, data = homes_subset)


# If I wanted SLO to be the reference level then:
# I could use fct_relevel to specify a new reference level (within tidyverse package), and could specify the order by continuing to add the order i want after SLO...

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

lm_slo <- lm(Price ~ City + SqFt, data = new_homes_subset)

summary(lm_slo)

```

AJ has been assigned as the city reference level
Our R squared value tells me that "53 % of variance in home price is explained by this model"

### Explore correlations between quantitative variables

Task: Make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price trhough SqFt).

We do this because we can't use pearson's R for non-quantitative variables like Status

```{r}
homes_quant <- homes_subset %>% 
select(Price:SqFt)

homes_core <- cor(homes_quant)

# Correlation matrix visualization

corrplot(homes_core, method = "ellipse") # <- color and direction are displayed with ellipse
```

### Compare AIC values

A lower AIC is better, they indicate a better fit model

```{r}
AIC(lm_1)
AIC(lm_2)
```

### Use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(lm_1, lm_2, lm_3))
```

### Use plot() to... make plots

```{r}
plot(lm_1)
```

#### Use broom::augment() to return the predictions for existing observations

```{r}
home_predictions <- augment(lm_1)
```

# Task: Make a histogram of the residuals from this model (lm_1)

```{r}
ggplot(data = home_predictions, aes(x = .resid)) + 
  geom_histogram()
```

# BRANCHES PRACTICE
